Static Analysis by Path Focusing

### 2011-06-03 report/report.tex
update of the report + minor changes in the code

@@

\begin{table}[!h]
\centering
\begin{tabular}{|c||c|c|c|c|} \hline 
Benchmark & Path Focusing & Lookahead Widening & Same invariant & Total \\
\hline \hline
automotive\_bitcount & 1 & 0 & 39 & 40 \\ \hline
automotive\_qsort1 & 7 & 3 & 6 & 16 \\ \hline
automotive\_susan\_c & 0 & 0 & 3 & 3 \\ \hline
automotive\_susan\_e & 0 & 0 & 3 & 3 \\ \hline
automotive\_susan\_s & 0 & 0 & 3 & 3 \\ \hline
bzip2d & 8 & 0 & 22 & 30 \\ \hline
bzip2e & 8 & 0 & 22 & 30 \\ \hline
consumer\_jpeg\_c & 25 & 9 & 694 & 728 \\ \hline
consumer\_jpeg\_d & 22 & 9 & 661 & 692 \\ \hline
consumer\_lame & 24 & 30 & 361  & 415 \\ \hline
consumer\_mad & 9 & 20 & 567 & 596 \\ \hline
consumer\_tiff2bw & 10 & 24 & 561 & 595 \\ \hline
consumer\_tiff2rgba & 8 & 25 & 457 & 490\\ \hline
consumer\_tiffdither & 9 & 23 & 560 & 592 \\ \hline
consumer\_tiffmedian & 10 & 24 & 609 & 643 \\ \hline
network\_patricia & 2 & 0 & 21 & 23 \\ \hline
office\_rsynth & 8 & 1 & 157 & 166\\ \hline
office\_stringsearch1 & 2 & 2 & 46 & 50\\ \hline
security\_blowfish\_d & 0 & 1 & 26 & 27\\ \hline
security\_blowfish\_e & 0 & 1 & 26 & 27\\ \hline
security\_rijndael\_d & 2 & 0 & 30 & 32\\ \hline
security\_rijndael\_e & 2 & 0 & 30 & 32\\ \hline
security\_sha  & 1 & 0 & 26 & 27\\ \hline
telecom\_adpcm\_c & 0 & 0 & 10 & 10\\ \hline
telecom\_adpcm\_d & 0 & 0 & 10 & 10\\ \hline
telecom\_CRC32 & 0 & 0 & 13 & 13\\ \hline
telecom\_gsm & 4 & 1 & 88 & 93\\ \hline
\end{tabular}
\caption{Number of basicblocks where the computed invariant is more precise with
\emph{Path Focusing}, \emph{Lookahead Widening}, or the same with both
techniques.}
\label{cbench}
\end{table}

@@

>>>>

	These benchmarks often contain non-linear arithmetic, especially
	multiplications. This is not a problem to the Apron library since it uses
	linearization to handle them, but this sometimes implies an execution time
	blowup for the SMT-solver:
\begin{itemize}
\item \emph{Yices} does not work at all when the formula contains non-linear
arithmetic, so we could not use it. Indeed, Linear Real Arithmetic or Linear
Integer Arithmetic theories do not treat multiplications.
\item \emph{Z3} implements some linearization techniques 
in order to deal with non-linear
arithmetic, even if the used theory is LRA or LIA. In lots of cases, it is
sufficient for deciding the satisfiability of our formulae, but it seems
sometimes to have a huge execution time blowup. 
When running our benchmarks, we fixed a time limit (5 minutes) for the analysis,
and ignore in our results the functions that make the SMT-solver blow.
\end{itemize}
	This drawback could be solved in the future, by linearizing parts of the
	SMT-formula that make the computation too costly, or make it fail (in some
	cases, the SMT-solver is unable to decide the satisfiability of the formula,
	and answers ``unknown'').

@@

\begin{table}[!h]
\centering
\begin{tabular}{|c||c|c|c|c|} \hline 
Benchmark & Path Focusing & Lookahead Widening & Same invariant & Total \\
\hline \hline
automotive\_bitcount	& 1 & 0 & 39 & 40 \\ \hline
automotive\_qsort1		& 7 & 0 & 9 & 16 \\ \hline
automotive\_susan\_c	& 0 & 0 & 3 & 3 \\ \hline
automotive\_susan\_e	& 0 & 0 & 3 & 3 \\ \hline
automotive\_susan\_s	& 0 & 0 & 3 & 3 \\ \hline
bzip2d					& 8 & 0 & 22 & 30 \\ \hline
bzip2e					& 8 & 0 & 22 & 30 \\ \hline
consumer\_jpeg\_c		& 35 & 0 & 693 & 728 \\ \hline
consumer\_jpeg\_d		& 30 & 0 & 662 & 692 \\ \hline
consumer\_lame			& 31 & 12 & 372  & 415 \\ \hline
consumer\_mad			& 9 & 8 & 579 & 596 \\ \hline
consumer\_tiff2bw		& 18 & 1 & 576 & 595 \\ \hline
consumer\_tiff2rgba		& 19 & 1 & 574 & 594\\ \hline
consumer\_tiffdither	& 17 & 1 & 574 & 592 \\ \hline
consumer\_tiffmedian	& 21 & 2 & 620 & 643 \\ \hline
network\_patricia		& 2 & 0 & 21 & 23 \\ \hline
office\_rsynth			& 8 & 0 & 158 & 166\\ \hline
office\_stringsearch1	& 5 & 1 & 44 & 50\\ \hline
security\_blowfish\_d	& 4 & 0 & 23 & 27\\ \hline
security\_blowfish\_e	& 4 & 0 & 23 & 27\\ \hline
security\_rijndael\_d	& 2 & 0 & 30 & 32\\ \hline
security\_rijndael\_e	& 2 & 0 & 30 & 32\\ \hline
security\_sha			& 1 & 0 & 26 & 27\\ \hline
telecom\_adpcm\_c		& 0 & 0 & 10 & 10\\ \hline
telecom\_adpcm\_d		& 0 & 0 & 10 & 10\\ \hline
telecom\_CRC32			& 0 & 0 & 13 & 13\\ \hline
telecom\_gsm			& 4 & 0 & 89 & 93\\ \hline
\end{tabular}
\caption{Number of basicblocks where the computed invariant is more precise by
\emph{Path Focusing}, \emph{Lookahead Widening}, or the same with both
techniques.}
\label{cbench}
\end{table}

@@

We compare \emph{Lookahead Widening} and \emph{Path Focusing} on various
GNU projects ( see Table \ref{opensource}), so that we can see their precision
on really used code.

\begin{table}
\centering
\begin{tabular}{|c||c|c|c|c|} \hline 
Benchmark & Path Focusing & Lookahead Widening & Same invariant & Total \\
\hline \hline
Bc			& 0 & 0 & 177 & 177 \\ \hline
Gawk		& 4 & 0 & 287 & 291 \\ \hline
Gnuchess	& 16 & 16 & 1447 & 1479 \\ \hline
Gnugo		& 120 & 10 & 1286 & 1416 \\ \hline
Grep		& 4 & 1 & 326 & 331 \\ \hline
Gzip		& 16 & 8 & 207 & 231 \\ \hline
Make		&  5 & 5 & 304 & 314 \\ \hline
Tar			& 13 & 2 & 437 & 452 \\ \hline
Wget		& 20 & 3 & 751 & 774 \\ \hline
\end{tabular}
\caption{Result of the analysis of various open-source projects.}
\label{opensource}
\end{table}
